The \dealii{} Library, Version 9.3

### 2021-04-23 9.3/paper.tex
Fix a grammar error.

\item \texttt{step-71} focused on automatic and symbolic
  differentiation (AD and SD, in short) as a tool to make solvers for complex, nonlinear
  problems possible. To this end, \dealii{} can interface to a number
  of AD and SD libraries, including Trilinos' Sacado package
  \cite{...}, ...\todo{which others??}, and SymEngine \cite{symengine-web-page}. The tutorial
  illustrates how these techniques can be used to compute derivatives
  of first a rather simple function, and then of the much more complex
  energy functions of two magneto-elastic and magneto-visco-elastic
  material formulations in which just the scalar energy functional
  takes up the better part of a page, and even first derivatives can
  only be computed with heroic effort.

>>>>

\item \texttt{step-71} focuses on automatic and symbolic
  differentiation (AD and SD, in short) as a tool to make solvers for complex, nonlinear
  problems possible. To this end, \dealii{} can interface to a number
  of AD and SD libraries, including Trilinos' Sacado package
  \cite{...}, ...\todo{which others??}, and SymEngine \cite{symengine-web-page}. The tutorial
  illustrates how these techniques can be used to compute derivatives
  of first a rather simple function, and then of the much more complex
  energy functions of two magneto-elastic and magneto-visco-elastic
  material formulations in which just the scalar energy functional
  takes up the better part of a page, and even first derivatives can
  only be computed with heroic effort.
